---
title: "Student Hustle Data Preparation"
output: pdf_document
author: "Dprep Team 3"
date: '2022-03-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(assertive)
library(dplyr)
library(googledrive)
library(readr)
library(knitr)
tinytex::install_tinytex()
```

## Data Retrieval
We have downloaded our data from [Inside Airbnb](http://insideairbnb.com/get-the-data.html). The aim of our research is to investigate which European student city is the best city to rent out your student room on Airbnb. We have focused on the top 10 European student cities. To further investigate our topic we retrieved the following data sets:

1. Detailed Listings data for Barcelona
2. Detailed Listings data for Berlin
3. Detailed Listings data for Copenhagen
4. Detailed Listings data for Dublin
5. Detailed Listings data for Edinburgh
6. Detailed Listings data for London
7. Detailed Listings data for Manchester
8. Detailed Listings data for Munich
9. Detailed Listings data for Paris
10. Detailed Listings data for Vienna

This data has been merged into one large dataset, which resulted in a dataset of 191.755 observations and 75 variables.

## Data Selection
To dig deeper into our research topic, we have chosen variables that could help answer our research question: **In which European city is renting out a private room on Airbnb most attractive in terms of income, ratings, and coverage?** The following variables are selected:

### Name
This variable shows the name of the listing. This variable gives clarity of the listings. 

### Host listings count
The focus is on students that are renting out their student room. A student (normally) has 1 student room. Therefore, we filter on hosts that have 1 listing. 

### Neighbourhood group cleansed
Despite the fact that we will not go deeper into the neighborhoods now due to time constraints, other stakeholders can explore the data set further by looking in which neighborhood it is best to rent out your student room.

### City
We focus on the 10 most popular student cities in Europe based on a research of [QS Top Universities](https://www.topuniversities.com/best-student-cities). The top 10 cities are:
1.  London    
2.  Munich    
3.  Berlin    
4.  Paris     
5.  Zurich    
6.  Vienna    
7.  Edinburgh 
8.  Barcelona 
9.  Dublin    
10. Manchester

### Property type
We first investigated what types of rooms there were by creating a table including all types of properties. After that, we filtered on student rooms, which are all the different types of private rooms. 

```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#Download the files through google drive

data_id <-"1p-4gvEglcpfqD9qkLsU0oAsCDOBKgjZNHG4QfXOFaS0"
drive_download(as_id(data_id), path = "airbnb_europe.csv", overwrite = TRUE)

#read the airbnb file

df <- read_csv("airbnb_europe.csv")

urls <- as.character(df$link)

datasets <- lapply(urls, function(url) {
  print(paste0('Now downloading ... ', url))
  city = tolower(as.character(df$city[match(url, df$link)]))
  
  res = read_csv(url)
  res$city <- city
  return(res)
})

#Combine the data into 1 dataset

downloaded_data = do.call('rbind', datasets) 

#Export to csv

write.csv(downloaded_data, 'downloaded_data.csv')

#Read csv
downloaded_data <- read.csv("downloaded_data.csv")

#Select the data we need to use for our research

student_data <- downloaded_data %>%
  select("name", "host_listings_count", "neighbourhood_group_cleansed", "city", "property_type", "price", "availability_365", "maximum_nights", "number_of_reviews", "review_scores_rating")

filtered_data <- student_data %>%
  filter(host_listings_count == 1, number_of_reviews >23, availability_365 >0)

private_room <- filtered_data %>% filter(grepl('Private room in bungalow|Private room in cabin|Private room in casa particular|Private room in castle|Private room in chalet Private room|Private room in condominium (condo)|Private room in cottage|Private room in floor|Private room in guest suite|Private room in guesthouse|Private room in hostel|Private room in houseboat|Private room in loft|Private room in rental unit|Private room in residential home|Private room in serviced apartment|Private room in tiny house|Private room in townhouse|Private room in treehouse|Private room in villa', property_type))

```
In the table below, you can find the different private rooms where we finally filtered on.

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
table(private_room$property_type)
```

### Price
The next variable is price, we would like to know what the mean prices are in each city to compare and know what a student can ask for their student room. First, there is investigated what the class of price is. The class was a character because of the dollar sign. Then we removed the dollar sign and the class changed to numeric. The next step was to check if there are any observations without a price. There were only 9 NA values, therefore we chose to delete them. After that, we calculated the mean prices per city, which can be found below.

```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
private_room$price = as.numeric(gsub("\\$", "", private_room$price))
private_room <- private_room[!is.na(private_room$price), ]
```

```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
mean_price_cities <- aggregate(private_room$price, list(private_room$city), FUN=mean)
names(mean_price_cities)[1]<- "city"
names(mean_price_cities)[2]<- "mean_price"
```

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
knitr::kable(mean_price_cities, format="markdown")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#Change the currency from DKK to euro

mean_price_cities_euro <- mean_price_cities %>%
  mutate(mean_price = case_when(city == 'copenhagen' ~ mean_price * 0.10,
                                TRUE ~ as.numeric(mean_price)))

#Change pound to dollar

mean_price_cities_euro1 <- mean_price_cities_euro %>%
  mutate(mean_price = case_when(city == 'london' ~ mean_price / 1.19,
    TRUE ~ as.numeric(mean_price))) %>%
      mutate(mean_price = case_when(city == 'manchester' ~ mean_price / 1.19,
        TRUE ~ as.numeric(mean_price))) %>%
          mutate(mean_price = case_when(city == 'edinburgh' ~ mean_price / 1.19,
            TRUE ~ as.numeric(mean_price)))
```

We encountered that the amount for Copenhagen was extremely high compared to the other cities. We assumed that this was because of the difference currency. Therefore, we changed all not europe currencies to euro currencies. At the moment of writing, 1 Danish Krone is 0.10 euros and 1 pound is 1.19 euros. Therefore we multiplied the mean price of Copenhagen by 0.10 and divided Edinburgh, London and Manchester by 1.19. The final mean prices per city are shown in the table below. 

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
knitr::kable(mean_price_cities_euro1, format="markdown")
```

### Availability 365
The availability is how many day a hosting is available to rent on Airbnb. We filtered on available above 0 as we only want to see listings that were available. As a student, you are only available in the weekends which is approximately 2 nights per week. Which is 104 days a year. We would like to investigate if this would cause any problems when renting out your student room. Also, we wanted  to know what the mean available days are on Airbnb, which can be found in the table below.

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#calculate the mean availability per city
mean_availability <- aggregate(private_room$availability_365, list(private_room$city), FUN=mean)
names(mean_availability) [1]<- "city"
names(mean_availability) [2]<- "mean_availability"
```
```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
knitr::kable(mean_availability, format="markdown")
```

### Maximum nights
To further elaborate on the previous variable. The maximum nights are 2 nights. Therefore, we included this variable as a dummy. 
Short stay (maximum of 2 nights) = 0
Long stay = 1

```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
#create a dummy for short stay 
short_stay <- ifelse(private_room$maximum_nights <= 2, 1, 0)
private_room <- data.frame(private_room,
                           short_stay)
```

### Number of reviews
We want to check the number of reviews, because if someone only has 1 review which is a 5, this cannot be seen as reliable. Therefore, we checked the maximum, minimum and mean number of reviews. Based on that, we filter above the mean number of reviews. 

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
max(student_data$number_of_reviews)
min(student_data$number_of_reviews)
mean(student_data$number_of_reviews)
```

### Review scores rating
Lastly, review scores rating is our dependent variable. This variable becomes our determinant to find out which city is the best to rent out your student room. 
